Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-02-07 manuscript/tables&figures.Rmd
highlighted dAICc values >1 and >2 in Table 4

```{r Table 1, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/table1_hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "Table 1. Summary of hypotheses, corresponding specific predictions, and results. We count predictions as fully supported ('yes') when the response is signficant in univariate models and included in all top multivariate models and as partially supported ('(yes)') or rejected ('(no)') when the direction of response consistently matched the prediction but  the effect was not significant in all models.") %>%
  pack_rows("Tree size and microenvironment", 1, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Larger, taller trees have lower Rt.", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Trees with more exposed crowns have lower Rt.", 3, 4, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Small trees (lower root volume) in drier microhabitats have lower Rt.", 5, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Species traits", 6, 10, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Species' traits--particularly leaf hydraulic traits--predict Rt.", 6, 10, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(1, width = "12cm") %>%
  column_spec(2:5, width = "1.2cm") %>%
  column_spec(6, width = "2.4cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5) %>%
  kableExtra::landscape()
```
\clearpage

@@

\clearpage
```{r table 4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
univar_table <- read.csv("tables_figures/table4_univariate_models.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_best_coeff.csv`.
kable(univar_table, booktabs = TRUE, caption = "Table 4. Single-variable tests of hypothesized drivers of drought resistance. Models including each variable were compared to corresponding null models. dAIC is the AICc of the null model minus that of the model including the variable (thus, dAICc>2 indicates that the variable significantly improves the model", format = 'latex', escape = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  pack_rows("Tree size and microenvironment", 1, 12, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Species traits", 13, 18, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  #mutate(dAICc = cell_spec(dAICc, "html", bold = ifelse(dAICc > 1.999, TRUE, FALSE))) %>%  #trying to put sig values in bold, but this doen't work
  kable_styling()
```

>>>>

```{r Table 1, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/table1_hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "Table 1. Summary of hypotheses, corresponding specific predictions, and results. We count predictions as fully supported ('yes') when the response is signficant in univariate models and included in all top multivariate models and as partially supported ('(yes)') or rejected ('(no)') when the direction of response consistently matched the prediction but  the effect was not significant in all models.") %>%
  pack_rows("Tree size and microenvironment", 1, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Larger, taller trees have lower Rt.", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Trees with more exposed crowns have lower Rt.", 3, 4, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Small trees (lower root volume) in drier microhabitats have lower Rt.", 5, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Species traits", 6, 10, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Species' traits--particularly leaf hydraulic traits--predict Rt.", 6, 10, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(1, width = "12cm") %>%
  column_spec(2:5, width = "1.2cm") %>%
  column_spec(6, width = "2.4cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5) %>%
  kableExtra::landscape()
```

\clearpage

@@

\clearpage
```{r table 4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
univar_table <- read.csv("tables_figures/table4_univariate_models.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_best_coeff.csv`.
kable(univar_table, booktabs = TRUE, caption = "Table 4. Single-variable tests of hypothesized drivers of drought resistance. Models including each variable were compared to corresponding null models. dAIC is the AICc of the null model minus that of the model including the variable (thus, dAICc>2 indicates that the variable significantly improves the model", format = 'latex', escape = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  pack_rows("Tree size and microenvironment", 1, 12, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Species traits", 13, 18, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  #mutate(dAICc = cell_spec(dAICc, "html", bold = ifelse(dAICc > 1.999, TRUE, FALSE))) %>%  #trying to put sig values in bold, but this doen't work
  kable_styling()
```
*dAICc > 1: variable qualified for inclusion in full model

**dAICc > 2: statistically signficant, variable qualified for inclusion in full model
